better title eventually

### 2015-05-11 cs261n-paper/paper.tex
added in survey questions

Talk about the basic methods of censoring, and how it differs 
around the world, which sites are targeted, etc.

Scope the paper here. Talk about how we are not up Cuba-like adversaries.

\section{UX sprint}  %%%%
\indent \indent Talk about it just enough that it makes a good storyline for the experiment that we 
are proposing a design of. Motivate it a little bit, and tell a story.

Appendix ~\ref{sec:pilot}.

@@

\subsection{Overview} %%%
Our experiment consists of three parts: informing and motivating the participants in order 
to roleplay in the experiment, asking our participants to complete a set of web browsing tasks which will 
require them to circumvent censorship using the Tor Browser, and soliciting feedback from our participants
about their experience. With participants' consent, we will also record their computer screen to monitor 
their activity and employ a browser extension to take empirical measurements (such as idle waiting time, 
how fast a particular task was completed, etc.) throughout the duration of this experiment.

@@

 %% what we will recruit for, how we inform, and interactions.

@@

%question breakdown
\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item 2 session and participant information questions
\item 4 basic demographics questions
\item 5 questions regarding their experience
\item 2 technical calibration questions
\item 4 Internet attitude questions
\end{itemize}

@@

\noindent Recall that the survey consists of the following 17 questions, in this order: 
\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item 2 session and participant information questions
\item 4 basic demographics questions
\item 6 questions regarding their experience with Tor
\item 2 technical calibration questions
\item 4 Internet attitude questions
\end{itemize}

\noindent Specifically, the questions are as follows: 
\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
\item foo
\item bar
\item baz
\item foo
\item bar
\item baz
\item foo
\item bar
\item baz
\item foo
\item bar
\item baz
\item foo
\item bar
\item baz
\item foo
\item bar
\end{enumerate}

>>>>

{\color {red} Talk about the basic methods of censoring, and how it differs 
around the world, which sites are targeted, etc.

Scope the paper here. Talk about how we are not up Cuba-like adversaries. }

\section{UX sprint}  %%%%
\indent \indent {\color {red} Talk about it just enough that it makes a good storyline for the experiment that we 
are proposing a design of. Motivate it a little bit, and tell a story.

Appendix ~\ref{sec:pilot}. }

@@

\subsection{Overview} 
Our experiment consists of three parts: informing and motivating the participants in order 
to roleplay in the experiment, asking our participants to complete a set of web browsing tasks which will 
require them to circumvent censorship using the Tor Browser, and soliciting feedback from our participants
about their experience. With participants' consent, we will also record their computer screen to monitor 
their activity and employ a browser extension to take empirical measurements (such as idle waiting time, 
how fast a particular task was completed, etc.) throughout the duration of this experiment.

@@

{\color {red} what we will recruit for, how we inform, and interactions.}

@@

%question breakdown
\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item 2 session and participant information questions
\item 4 basic demographics questions
\item 5 questions regarding their experience with Tor
\item 4 Internet attitude questions
\item 2 technical calibration questions
\end{itemize}

@@

\noindent Recall that the survey consists of the following 17 questions, in this order: 
\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item 2 session and participant information questions
\item 4 basic demographics questions
\item 5 questions regarding their experience with Tor
\item 4 Internet attitude questions
\item 2 technical calibration questions
\end{itemize}

\noindent Specifically, the questions are as follows: 
\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
\item What session did you attend?  
\item What is your participant ID? (This can be found on the sticker on the left hand corder of desk you are currently sitting at.) \\
\item What is your gender? 
\item What is your age? 
\item Please select your highest level of education. 
\item What is your current occupation? \\
\item How familiar were you with Tor prior to this study? 
\item Were you confident that Tor was able to provide you with security and anonymity while completing your tasks?
\item Did anything unexpected happen while using Tor? 
\item What, if any, of the following could use improvement? 
\item Based on your experience, would you use Tor again? \\
\item How many hours a week would you say you spend on the internet? 
\item How concerned are you about your privacy on the Internet?
\item How concerned are you about staying anonymous on the internet?
\item How concerned are you about being censored while you browse the Internet? \\
\item How familiar are you with computer security? 
\item What kinds of computer security software do you use? 
\end{enumerate}
